---
title: "GC Draft Plot"
output: 
  html_document:
    keep_md:true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## Ring-tailed lemur fecal glucocorticoids

Read in processed data

```{r}
library(tidyverse)
library(googlesheets4)

aggGC_full <- read_sheet("https://docs.google.com/spreadsheets/d/12EB2WXBiqfwHPIQ_2tqOvkV0i8Yzjoc5yhMlkAOtUv0/edit?usp=sharing")
```

## Targeted plots & analysis 
1. Seasonality of GC in adults:
    Do GC's change predictably with reproductive state in females (gestation, lactation, weaning, etc)
    
```{r}
library(gghalves)
library(lme4)
library(car)

aggGC_full %>% filter(!is.na(season), age.2wk > 150) %>% 
ggplot()+
  geom_half_boxplot(aes(x = season, y = log(mean.ngg), color = sex), side = "r")+
  geom_half_point(aes(x = season, y = log(mean.ngg), color = sex), side = "l", alpha = 0.6)+
  ggtitle("Fecal GC in RTL older than 150 weeks")
  theme_bw()

aggGC_full.noNA <- aggGC_full %>% filter(!is.na(season))

adultSeason.lm <- lmer(log(mean.ngg)~season*sex + (1|an.id), data = aggGC_full.noNA[aggGC_full.noNA$age.2wk > 150, ])
Anova(adultSeason.lm)
summary(adultSeason.lm)

```

A mixed effects linear model shows only a signficant effect of sex on fecal GC's. Not of season, and there is no interaction between season & sex.

2. Aggression rates in adults across season & sex

```{r}

aggRc <- aggGC_full %>% filter(!is.na(season), age.2wk > 150) %>% 
ggplot()+
  geom_half_boxplot(aes(x = season, y = log(wkAggRcv.rt), color = sex), side = "r")+
  geom_half_point(aes(x = season, y = log(wkAggRcv.rt), color = sex), side = "l", alpha = 0.6)+
  theme_bw()+
  theme(legend.position = c(0.1, 0.85))

aggDt <- aggGC_full %>% filter(!is.na(season), age.2wk > 150) %>% 
ggplot()+
  geom_half_boxplot(aes(x = season, y = log(wkAggress.rt), color = sex), side = "r")+
  geom_half_point(aes(x = season, y = log(wkAggress.rt), color = sex), side = "l", alpha = 0.6)+
  theme_bw()+
    theme(legend.position = "none")

library(cowplot)
plot_grid(aggRc, aggDt, nrow = 2)

adultSeasonAggRc.lm <- lmer(wkAggRcv.rt~season*sex + (1|an.id), data = aggGC_full)
Anova(adultSeasonAggRc.lm)
summary(adultSeasonAggRc.lm)


```

3. Fecal GC ~ Age in weeks * sex

```{r}

agePlot <- aggGC_full %>% dplyr::filter(age.2wk <= 150) %>%
  ggplot()+
  geom_point(aes(x = age.2wk, y = log(mean.ngg), color = sex), alpha = 0.6)+
  geom_smooth(aes(x = age.2wk, y = log(mean.ngg), color = sex))+
  theme_bw()


bplot <- aggGC_full %>% dplyr::filter(age.2wk <= 150) %>%
  ggplot()+
  geom_half_boxplot(aes(x = ageClass, y = log(mean.ngg), color = sex), side = "r")+
  geom_half_point(aes(x = ageClass, y = log(mean.ngg), color = sex), side = "l", alpha = 0.6)+
  theme_bw()

plot_grid(agePlot, bplot, nrow = 2)

```


4. Aggression Received & Dealt ~ Age in weeks * sex


